Summarize distribution of LR statistic under null

### 2016-12-20 analysis/checkIP.Rmd
Working on revisions to CompareEEvsETmodel.Rmd.
Successfully knit summarize_dsc_znull.Rmd using simulation results from res.znull.RData.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

We want to compare the likelihoods achieved by the newly implemented interior point method with the EM algorithm.

@@

The 'dsc-opt' simply runs both methods (IP and EM) on the same data sets, 
and compares the difference in the log-likelihoods. We can see that
in >90% of cases the difference is negligible. Then there is a tail of
cases where the IP loglik is higher - presumably where the EM doesn't really converge so well.

```{r}
  load("../output/dsc-opt-files/dsc_opt.RData")
  plot(ecdf(dsc_opt$res$diff1),main="ECDF of log-likelihood difference (IP-EM)")
```

@@

```{r}
  load("../output/dsc-shrink-files/res.RData")
  library("ggplot2")
  library("dplyr")
  library("reshape2")
  # select out the lfsr estimates for each method

  df1 = res$lfsr %>% dplyr::filter(method %in% c("ash.hu.nocxx")) %>% select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="lfsr.nocxx")
  df2 = res$lfsr %>% dplyr::filter(method %in% c("ash.hu")) %>% select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="lfsr.IP")

  df = inner_join(df1,df2,by=c("scenario","seed","variable"))
  ggplot(df,aes(lfsr.nocxx,lfsr.IP)) +geom_point(shape=1) +
  facet_wrap(~ scenario, nrow=2) + 
  geom_abline(colour = "black") +
  xlab("EM algorithm (no cxx)") +
  ylab("IP method")
```

>>>>

Here we compare the likelihoods achieved by the newly implemented
interior point method against the EM algorithm.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
source("chunk-options.R")
```

@@

The 'dsc-opt' script simply runs both methods (IP and EM) on the same data sets,
and compares the difference in the log-likelihoods. We can see that in >90% of 
cases the difference is negligible. Then there is a tail of cases where the IP 
log-likelihood is higher - presumably where the EM doesn't really converge so
well.

```{r compare_likelihoods}
load("../output/dsc-opt-files/dsc_opt.RData")
plot(ecdf(dsc_opt$res$diff1),
     main = "ECDF of log-likelihood difference (IP - EM)")
```

@@

```{r compare_lfsr}
load("../output/dsc-shrink-files/res.RData")

# Select out the lfsr estimates for each method.
df1 = res$lfsr %>% filter(method %in% c("ash.hu.nocxx")) %>% 
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.nocxx")
df2 = res$lfsr %>% filter(method %in% c("ash.hu")) %>%
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.IP")
df = inner_join(df1,df2,by = c("scenario","seed","variable"))
ggplot(df,aes(lfsr.nocxx,lfsr.IP)) + geom_point(shape = 1) +
facet_wrap(~ scenario,nrow = 2) +
geom_abline(colour = "black") +
xlab("EM algorithm (no cxx)") +
ylab("IP method")
```

### 2016-12-20 analysis/investigate_hu_badcoverage.Rmd
Successfully knit summarize_dsc_znull.Rmd using simulation results from res.znull.RData.

```{r chunk_options, include=FALSE}
source("chunk-options.R")
```

@@

library("dscr")
library("ashr")
library(reshape2)
library(ggplot2)
library(dplyr)

neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="negprob") %>%
    filter(negprob > 0.95)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="posprob") %>%
    filter(posprob > 0.95)

reslong = 
  res$cdf_score %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%    
    melt(id.vars=c("method","scenario","seed",".id"))

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

@@

out <- res$negprob
neglong = 
  out %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name = "negprob") %>%
    filter(negprob > 0.95)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),value.name="posprob") %>%
    filter(posprob > 0.95)

reslong = 
  res$cdf_score %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%    
    melt(id.vars = c("method","scenario","seed",".id"))

### 2016-12-20 analysis/summarize_dsc_znull.Rmd
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.
Successfully knit summarize_dsc_znull.Rmd using simulation results from res.znull.RData.

---
title: "Summarize distribution of LR statistic under null"
author: "Matthew Stephens"
date: 2015-10-26
---

@@

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

```{r}
library(ggplot2)
library(dplyr)
load("../output/dsc-znull-files/res.znull.RData")
temp=ungroup(res %>% group_by(scenario,method) %>% summarise(gt0=mean(logLR>0)))
xtabs(gt0~method+scenario,temp)

```

Note that the ash.n.s conforms closely to the null expectation
of 0.5 chi2_0 +0.5 chi2_1 from Stram and Lee, Biometrics

conjecture: the uniform has the same asymptotic behaviour
and the half uniform is like the sum of two of these?

@@

```{r}
ggplot(res %>% filter(logLR>0) %>% filter(grepl("ash.hu",method)) , aes(sample = logLR)) + facet_grid(scenario~method) +
  stat_qq(dist = qchisq, dparams=list(df=1)) + geom_abline() + ggtitle("qqplot under null vs chisq-1; line slope=1")
ggplot(res %>% filter(logLR>0) %>% filter(grepl("ash.u",method)) , aes(sample = logLR)) + facet_grid(scenario~method) +
  stat_qq(dist = qchisq, dparams=list(df=1)) + geom_abline(intercept=0,slope=0.5) + ggtitle("qqplot under null vs chisq-1; line slope=0.5")
ggplot(res %>% filter(logLR>0) %>% filter(grepl("ash.n",method)), aes(sample = logLR)) + facet_grid(scenario~method) +
  stat_qq(dist = qchisq, dparams=list(df=1)) + geom_abline(intercept=0,slope=0.5) + ggtitle("qqplot under null vs chisq-1; line slope=0.5")

```

>>>>

---
title: "Summarize distribution of LR statistic under null"
author: "Matthew Stephens"
date: '2015-10-26'
---

@@

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

Load and summarize the results of the data simulations.

```{r load_sim_results}
load("../output/dsc-znull-files/res.znull.RData")
out <- ungroup(res %>% group_by(scenario,method) %>% 
                  summarise(gt0 = mean(logLR > 0)))
xtabs(gt0 ~ method + scenario,out)
```

Note that the ash.n.s conforms closely to the null expectation of 0.5 
chi2_0 + 0.5 chi2_1 from Stram and Lee, Biometrics.

*Conjecture:* the uniform has the same asymptotic behaviour and the half 
uniform is like the sum of two of these?

@@

```{r scatterplots}
ggplot(res %>% filter(logLR > 0) %>% filter(grepl("ash.hu",method)),
       aes(sample = logLR)) + 
  facet_grid(scenario ~ method) +
  stat_qq(distribution = qchisq,dparams = list(df=1)) + 
  geom_abline() + 
  ggtitle("qqplot under null vs chisq-1; line slope=1")

ggplot(res %>% filter(logLR > 0) %>% filter(grepl("ash.u",method)),
       aes(sample = logLR)) + 
  facet_grid(scenario~method) +
  stat_qq(distribution = qchisq,dparams = list(df = 1)) + 
  geom_abline(intercept = 0,slope = 0.5) + 
  ggtitle("qqplot under null vs chisq-1; line slope=0.5")

ggplot(res %>% filter(logLR > 0) %>% filter(grepl("ash.n",method)),
       aes(sample = logLR)) + 
  facet_grid(scenario ~ method) +
  stat_qq(distribution = qchisq,dparams = list(df = 1)) + 
  geom_abline(intercept = 0,slope = 0.5) + 
  ggtitle("qqplot under null vs chisq-1; line slope=0.5")
```
